Elimination Of Jump Objects

### 2022-06-29 paper/skeleton.tex
Update skeleton.tex

\documentclass[sigplan,review,11pt,nonacm,natbib=false]{acmart}
\settopmatter{printfolios=false,printccs=false,printacmref=false}
\usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false]{biblatex}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{ffcode}
\usepackage{amsmath}

@@

\keywords{Object-Oriented Programming, software engineering, algorithms, computer science}

@@

It consists of the goto atom-object, the abstract object \emph{g}, and the g.forward attribute. Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.forward} can be called to each of them.

@@

\begin{equation}
\begin{split}
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{forward}(\delta_1), TRUE ) \rrbracket) 
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
\end{split}
\end{equation}

\begin{equation}
\begin{split}
& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \delta_2, \delta_1) \rrbracket) \\
\end{split}
\end{equation}

\begin{equation}
\begin{split}
& \ff{if.}(\mu_1.not, \delta_2, \delta_1) \\
\end{split}
\end{equation}

@@

\begin{equation} \nonumber
\begin{split}
& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
\end{split}
\end{equation}

\hline

\begin{equation} \nonumber
\begin{split}
& \ff{if.}(\mu_1.not, \delta_2, \delta_1) \\
\end{split}
\end{equation}

To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto forward.

@@

Let's denote lines \ref{ln:ret0}-\ref{ln:ret1} as X.

@@

Also, after replacing the jump, we must create an additional \emph{flag} object, which will be changed if the jump condition is met, i.e. when in the new if-statement, the 'ELSE' branch will be executed - value of flag will change. This is required so that all objects following the if-statement that are attributes of the abstract object g are not executed.
So, by wrapping each object following the jump condition and whose nesting is at least that of the g object in an if-statement with a flag value check condition, we make sure that these objects will not be executed when the jump condition is met.

By swapping the statements that follow the if-statement body and after the jump itself, as described above, we get the following replacement for this example: the \m{1} object must be inverted with (\m{1}).not; in 'THEN' brunch of if-statement places \dlt{2}; in the 'ELSE' brunch creates new object seq, consisting of two elements - \dlt{1} and flag's value change, because the jump condition is satisfied.

@@

Let's denote lines \ref{ln:ret2}-\ref{ln:ret3} as X'.

Now let's look at an example program with nested objects containing goto forward:
\begin{ffcode}
goto
  [g]
    |\sgm{0}| > @
      X
      |\sgm{4}|
\end{ffcode}

@@

The language currently provides a while generator, on which other generators are implemented.

The simplest way to call goto forward inside a while-loop is represented as:

\begin{equation}
\begin{split}
& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \\
& \quad ) \\
& \rrbracket) \\
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{while}.(\ff{and}.( \\
& \quad \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
& \quad \quad \ff{if}.(\mu_1,  \ff{g}.\ff{forward}(\delta_1), \delta_2) \\
& \quad ) \\
& \rrbracket) \\
\end{split}
\end{equation}

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{while}.(\ff{and}.( \\
& \quad \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
& \quad \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \\
& \quad \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) )\\
& \quad \quad ) \\
& \quad ) \\
& \rrbracket) \\
\end{split}
\end{equation}

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{while}.(\ff{and}.( \\
& \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
& \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \\
& \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) )\\
& \quad ) \\
& ) \\
\end{split}
\end{equation}

@@

\begin{equation} \nonumber
\begin{split}
& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \\
& \quad ) \\
& \rrbracket) \\
\end{split}
\end{equation}

\hline

\begin{equation} \nonumber
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{while}.(\ff{and}.( \\
& \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
& \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \\
& \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) \\
& \quad )\\
& ) \\
\end{split}
\end{equation}

To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto forward.

@@

Let's denote lines \ref{ln:ret4}-\ref{ln:ret5} as Y.

@@

Since the jump is executed once the jump condition is true, the while loop will be executed as long as the jump condition is false. We can deduce that the condition for the jump is tested at every iteration of the loop, exactly the same as the condition in the while body itself.
So by combining the jump condition and the while loop condition do not violate the program logic. But the point is, once the jump condition is true, the next iteration of the while loop will fail and the loop will end.
So we only care about the first triggering of the jump condition for goto-forward. To do this, we can create an auxiliary object \emph{flag} that will be TRUE as soon as the jump condition is met.
Otherwise, all statements that came after the jump in the while loop will be executed.
So the combined condition of the while loop will look like: while (!flag AND condOfWhile).

Thus, the transformation is:

@@

Let's denote lines \ref{ln:ret6}-\ref{ln:ret7} as Y'.

@@

Same as with goto forward, there is the goto \emph{atom}-object, the abstract object \emph{g}, and the g.backward attribute. Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.backward} can be called to each of them.

@@

This is identical to that discussed in Section 3.1.1. In cases where the jump is performed without condition, you need to add an additional if-statement, similar to the example in Section 3.1.1:

\begin{equation}
\begin{split}
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{backward}, TRUE ) \rrbracket) \\
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \\
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \\
& \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \\
& \quad ) \\
& \rrbracket) \\
\end{split}
\end{equation}

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \\
& \quad \quad \ff{seq}(flag.\ff{write}(1), \\
& \quad \quad  \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
& \quad \quad ) \\
& \quad ) \\
& \rrbracket) \\
\end{split}
\end{equation}

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{while}.(\ff{eq}.(flag 0), \\
& \quad \ff{seq}(flag.\ff{write}(1), \\
& \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
& \quad ) \\
& ) \\
\end{split}
\end{equation}

@@

\begin{equation} \nonumber
\begin{split}
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \\
\end{split}
\end{equation}

\hline

\begin{equation} \nonumber
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{while}.(\ff{eq}.(flag 0), \\
& \quad \ff{seq}(flag.\ff{write}(1), \\
& \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
& \quad ) \\
& ) \\
\end{split}
\end{equation}

To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto backward.

@@

\begin{ffcode}
goto
  [g]
    |\sgm{1}||$\label{ln:ret8}$|
      |\sgm{2}|
      if.
        |\m{1}|
        g.backward
        |\dlt{1}|
      |\sgm{3}||$\label{ln:ret9}$|
\end{ffcode}

Let's denote lines \ref{ln:ret8}-\ref{ln:ret9} as W.

Note that goto-backward works the same as do-while construction in other languages: the first iteration of the new loop is always executed, and the next only if the condition is TRUE.
So, all objects that occurs between the declaration of an abstract object \emph{g} and the "jump" itself should be executed before the new while loop once, and all subsequent times were executed depending on the condition of the loop.

@@

Let's denote lines \ref{ln:ret10}-\ref{ln:ret11} as W'.

Let's look at an example of a chain of nested objects containing a goto backward:

@@

goto
  [g]
    |\sgm{0}|
      W
      |\sgm{4}|

@@

\begin{equation}
\begin{split}
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2) \\
& \quad ) \\
& \rrbracket) \\
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \\
& \quad \quad \ff{while}.(\mu_0, \\
& \quad \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \\
& \quad \quad ) \\
& \quad ) \\
& \rrbracket) \\
\end{split}
\end{equation}

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \\
& \quad \quad \ff{seq}(flag.\ff{write}(1), \\
& \quad \quad \quad \ff{while}.( \\
& \quad \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \\
& \quad \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
& \quad \quad \quad ) \\
& \quad \quad ) \\
& \quad ) \\
& \rrbracket) \\
\end{split}
\end{equation}

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{while}.(\ff{eq}.(flag 0), \\
& \quad \ff{seq}(flag.\ff{write}(1), \\
& \quad \quad \ff{while}.( \\
& \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \\
& \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
& \quad \quad ) \\
& \quad ) \\
&  ) \\
\end{split}
\end{equation}

@@

\begin{equation} \nonumber
\begin{split}
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2) \\
& \quad ) \\
& \rrbracket) \\
\end{split}
\end{equation}

\hline

\begin{equation} \nonumber
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{while}.(\ff{eq}.(flag 0), \\
& \quad \ff{seq}(flag.\ff{write}(1), \\
& \quad \quad \ff{while}.( \\
& \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \\
& \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
& \quad \quad ) \\
& \quad ) \\
&  ) \\
\end{split}
\end{equation}

To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto backward.

@@

To understand that the logic is not broken, let's look at a special case of calling goto backward inside a while-loop.

@@

Let's denote lines \ref{ln:ret12}-\ref{ln:ret13} as Z.

As described in section 3.2.2, the program runs from top to bottom until it meets goto forward and if the jump condition is met, the abstract object g is executed again.
Similar to what was said in section 3.2.2, all objects inside the abstract object g should be copied at the jump point.

The only difference, when the jump itself frames a while loop, is that when the jump condition is met, we need to interrupt the execution of all the internal while loops inside the new while loop, which we replaced the jump with.

In order to interrupt the execution of each of the internal while loops, we can add an additional condition to each of them, whether the jump condition is met or not. This can be done with an additional flag object that will signal for each inner while loop whether the jump condition has been met.

So, all internal while loops will not be executed further if flag shows that the jump condition is met and the logic of the program is not violated. For all other objects inside our new while loop, we should apply the transformation described in section 3.2.2.

The transformation will look like this:

@@

Let's denote lines \ref{ln:ret14}-\ref{ln:ret15} as Z'.

>>>>

\documentclass[sigplan,review,11pt,nonacm,natbib=false]{acmart}
\settopmatter{printfolios=false,printccs=false,printacmref=false}
\usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false]{biblatex}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{xcolor}

\usepackage[T2A,T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[russian,english]{babel}
  \renewcommand\ttdefault{cmtt}
\usepackage{csquotes}
\usepackage{ffcode}
\usepackage{CJKutf8}
\usepackage{paralist}
\usepackage{cancel} % to enable \cancel command
\usepackage{anyfontsize} % To get rid of font not found warnings
\usepackage{tabularx} % for special tables
\usepackage{amsmath}
\usepackage{to-be-determined}
\usepackage{href-ul}
\usepackage{amsthm}
\usepackage{tcolorbox} % for algorithm
  \tcbuselibrary{skins}
\usepackage{fdsymbol} % for \mathbb
\usepackage{algpseudocode} % for algorithms
\usepackage{multicol} % for two cols in BNF
\usepackage{pgffor} % to enable \foreach
\usepackage{stmaryrd}
\usepackage{mathtools}

\newcommand\br{\\[-4pt]}
\newcounter{rule}
\renewcommand\therule{R\arabic{rule}}
\newcommand\rr{\smalltriangleright{}}
\newcommand\rrule[1]{{\scshape\sffamily\ref{rule:#1}}}
\newcommand{\jrule}[1]{%
  \refstepcounter{rule}\label{rule:#1}%
  \text{\textbf{\rrule{#1}}}}

@@

@@

It consists of the goto \emph{atom}-object, the abstract object \emph{g}, and the g.forward attribute. Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.forward} can be called to each of them.

@@

\begin{equation}
\begin{split}
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing,\br
& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{forward}(\delta_1), TRUE ) \rrbracket)\\
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
& \quad \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \br
\end{split}
\end{equation}

\begin{equation}
\begin{split}
& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \delta_2, \delta_1) \rrbracket) \br
\end{split}
\end{equation}

\begin{equation}
\begin{split}
& \ff{if.}(\mu_1.\ff{not}, \delta_2, \delta_1) \br
\end{split}
\end{equation}

@@

\begin{equation*}
\dfrac
    {\begin{matrix}
    \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
    \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket)
    \end{matrix}}
    {\ff{if.}(\mu_1.\ff{not}, \delta_2, \delta_1)}
    \jrule{1}
\end{equation*}

To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-forward.

@@

Let's denote lines \ref{ln:ret0}-\ref{ln:ret1} as $X$.

@@

Also, after replacing the jump, we must create an additional \emph{flag} object, which will be changed if the jump condition is met, i.e. when in the new if-statement, the 'ELSE' branch will be executed - value of flag will change. This is required so that all objects following the if-statement that are attributes of the abstract object \emph{g} are not executed.
So, by wrapping each object following the jump condition and whose nesting is at least that of the \emph{g} object in an if-statement with a flag value check condition, we make sure that these objects will not be executed when the jump condition is met.

By swapping the statements that follow the if-statement body and after the jump itself, as described above, we get the following replacement for this example:
the \m{1} object must be inverted with (\m{1}).not;
in 'THEN' brunch of if-statement places \dlt{2}; in the 'ELSE' brunch creates new object \emph{seq}, consisting of two elements - \dlt{1} and flag's value change, because the jump condition is satisfied.

@@

Let's denote lines \ref{ln:ret2}-\ref{ln:ret3} as $X'$.

Now let's look at an example program with nested objects containing goto-forward:

\begin{ffcode}
goto
  [g]
    |\sgm{0}| > @
      X
      |\sgm{4}|
\end{ffcode}

@@

The language currently provides a \emph{while} generator, on which other generators are implemented.

The simplest way to call goto-forward inside a \emph{while}-loop is represented as:

\begin{equation}
\begin{split}
& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
& \quad \varphi \mapsto \ff{while}.(\mu_0, \br
& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) ) \rrbracket) \br
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
& \quad \varphi \mapsto \ff{while}.(\br
& \quad \quad \ff{and}.( \mu_0, \ff{eq}.(flag  1).\ff{not}), \br
& \quad \quad \ff{if}.(\mu_1,  \ff{g}.\ff{forward}(\delta_1), \delta_2) )\rrbracket)\\[-1pt]
\end{split}
\end{equation}

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
& \quad \varphi \mapsto \ff{while}.(\br
& \quad \quad \ff{and}.( \mu_0, \ff{eq}.(flag  1).\ff{not}), \br
& \quad \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \br
& \quad \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) ) ) ) \rrbracket )\\[-1pt]
\end{split}
\end{equation}

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{while}.(\br
& \quad \ff{and}.(\mu_0, \ff{eq}.(flag  1).\ff{not}), \br
& \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \br
& \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) ) ) ) \\[-1pt]
\end{split}
\end{equation}

@@

\begin{equation*}
\dfrac
    {\begin{matrix}
    & \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
    & \quad \varphi \mapsto \ff{while}.(\mu_0, \\
    & \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2))\rrbracket) \\
    \end{matrix}}
    {\begin{matrix}
    & \ff{memory}(flag), \\
    & flag.\ff{write}(0), \\
    & \ff{while}.(\ff{and}.( \\
    & \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
    & \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \\
    & \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0))) \\
    \end{matrix}}
    \jrule{2}
\end{equation*}

To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-forward.

@@

Let's denote lines \ref{ln:ret4}-\ref{ln:ret5} as $Y$.

@@

Since the jump is executed once the jump condition is true, the while loop will be executed as long as the jump condition is false. We can deduce that the condition for the jump is tested at every iteration of the loop, exactly the same as the condition in the while body itself.
So by combining the jump condition and the while loop condition do not violate the program logic. But the point is, once the jump condition is true, the next iteration of the while loop will fail and the loop will end.
So we only care about the first triggering of the jump condition for goto-forward. To do this, we can create an auxiliary object \emph{flag} that will be TRUE as soon as the jump condition is met.

If the jump condition is met, all objects inside the abstract object \emph{g} and following the goto-forward will not be executed. To do this, each of these objects should be wrapped in an additional if-statement, which will check the value of the flag, in other words - whether the jump condition is met or not.

Otherwise, all statements that came after the jump in the while loop will be executed.
So the combined condition of the while loop will be presented as: while (!flag AND condOfWhile).

Thus, the transformation will be presented as:

@@

Let's denote lines \ref{ln:ret6}-\ref{ln:ret7} as $Y'$.

@@

Same as with goto-forward, there is the goto \emph{atom}-object, the abstract object \emph{g}, and the g.backward attribute. Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.backward} can be called to each of them.

@@

This is identical case to that discussed in Section 3.1.1. In cases where the jump is performed without condition, we need to add an additional if-statement, similar to the example in Section 3.1.1:

\begin{equation}
\begin{split}
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{backward}, TRUE ) \rrbracket) \br
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
& \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \br
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
& \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ))\rrbracket) \\[-1pt]
\end{split}
\end{equation}

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
& \quad \quad \ff{seq}(flag.\ff{write}(1), \br
& \quad \quad  \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) )))\rrbracket) \\[-1pt]
\end{split}
\end{equation}

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{while}.(\ff{eq}.(flag 0), \br
& \quad \ff{seq}(flag.\ff{write}(1), \br
& \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ))) \\[-1pt]
\end{split}
\end{equation}

@@

\begin{equation*}
\dfrac
    {\begin{matrix}
    & \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
    & \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \\
    \end{matrix}}
    {\begin{matrix}
    & \ff{memory}(flag), \\
    & flag.\ff{write}(0), \\
    & \ff{while}.(\ff{eq}.(flag 0), \\
    & \quad \ff{seq}(flag.\ff{write}(1), \\
    & \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ))) \\
    \end{matrix}}
    \jrule{3}
\end{equation*}

To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-backward.

@@

\begin{ffcode}
goto
  [g]
    |\sgm{1}| > @ |$\label{ln:ret8}$|
      |\sgm{2}|
      if.
        |\m{1}|
        g.backward
        |\dlt{1}|
      |\sgm{3}||$\label{ln:ret9}$|
\end{ffcode}

Let's denote lines \ref{ln:ret8}-\ref{ln:ret9} as $W$.

Note that goto-backward works the same as do-while construction in other languages: the first iteration of the new loop is always executed, and the next only if the condition of loop is TRUE.
So, all objects that occurs between the declaration of an abstract object \emph{g} and the "jump" itself should be executed before the new while loop once, and all subsequent times were executed depending on the condition of the loop.

@@

Let's denote lines \ref{ln:ret10}-\ref{ln:ret11} as $W'$.

Let's look at an example of a chain of nested objects containing a goto-backward:

@@

goto
  [g]
    |\sgm{0}| > @
      W
      |\sgm{4}|

@@

\begin{equation}
\begin{split}
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
& \quad \varphi \mapsto \ff{while}.(\mu_0, \br
& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2))\rrbracket) \br
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
& \quad \quad \ff{while}.(\mu_0, \br
& \quad \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 )))\rrbracket) \\[-1pt]
\end{split}
\end{equation}

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
& \quad \quad \ff{seq}(flag.\ff{write}(1), \br
& \quad \quad \quad \ff{while}.( \br
& \quad \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \br
& \quad \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ))))\rrbracket) \\[-1pt]
\end{split}
\end{equation}

\begin{equation}
\begin{split}
& \ff{memory}(flag), \\
& flag.\ff{write}(0), \\
& \ff{while}.(\ff{eq}.(flag 0), \br
& \quad \ff{seq}(flag.\ff{write}(1), \br
& \quad \quad \ff{while}.( \br
& \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \br
& \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) )))) \\[-1pt]
\end{split}
\end{equation}

@@

\begin{equation*}
\dfrac
    {\begin{matrix}
    & \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
    & \quad \varphi \mapsto \ff{while}.(\mu_0, \\
    & \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2) ) \rrbracket ) \\
    \end{matrix}}
    {\begin{matrix}
    & \ff{memory}(flag), \\
    & flag.\ff{write}(0), \\
    & \ff{while}.(\ff{eq}.(flag 0), \\
    & \quad \ff{seq}(flag.\ff{write}(1), \\
    & \quad \quad \ff{while}.( \\
    & \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \\
    & \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) )))) \\
    \end{matrix}}
    \jrule{4}
\end{equation*}

To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-backward.

@@

To understand that the logic is not broken, let's look at an abstract case of calling goto-backward inside a while-loop.

@@

Let's denote lines \ref{ln:ret12}-\ref{ln:ret13} as $Z$.

Similar to the technique we used in section 3.1.3 with goto-forward inside the while loop, in this case, to avoid all subsequent iterations of the inside while loop, we combine its condition with the jump condition. As in Section 3.2.2, we create a global flag object, which will be an indicator of the execution of the jump condition. As soon as the jump condition is met, we change the flag value, and the next iteration of the inside while loop will fail during the check due to our added combined execution condition.

The rest of the transformation looks identical to that described in section 3.2.2: create a global while loop with a check for moisture values, Invert the jump condition and if the goto-backward condition is met, change the value of the flag object.
It is also necessary to wrap all objects that lie inside the abstract object \emph{g} in an additional if-statement with a check for the flag value, so that all of them are not fulfilled as soon as the jump condition is met.

The transformation will be presented as:

@@

Let's denote lines \ref{ln:ret14}-\ref{ln:ret15} as $Z'$.
